Results (Barcelona)

### 2022-01-03 docs/06_results-bcn.Rmd
Only Barcelona data

---
title: "Results"
output: github_document
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
draws <- gather_draws(model_fits$fit, `b_.*`, `sigma`, regex = TRUE)

@@

vcov(model_fits$fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text.y = element_text(hjust = 1, size = 7),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
	)

@@

m <- emmeans(model_fits$fit, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
	as_tibble() %>% 
	clean_names() %>% 
	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))

@@

m <- epred_draws(object = model_fits$fit, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(.value = logit_to_prob(.epred))

>>>>

---
title: "Results (Barcelona)"
output: github_document
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
draws <- gather_draws(model_fits$fit_bcn, `b_.*`, `sigma`, regex = TRUE)

@@

vcov(model_fits$fit_bcn) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text.y = element_text(hjust = 1, size = 7),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
	)

@@

m <- emmeans(model_fits$fit_bcn, ~trial_type:lp, by = "age_group", epred = TRUE) %>% 
	as_tibble() %>% 
	clean_names() %>% 
	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x < 0, 0, x)) %>% 
	mutate_at(vars(emmean:upper_hpd), function(x) ifelse(x > 1, 1, x))

@@

m <- epred_draws(object = model_fits$fit_bcn, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(.value = logit_to_prob(.epred))
